\documentclass{report}

\input{macros}
%
%\title{\nzmath User Manual\\ {\large{(for version 1.0)}}}
%\date{}
%\author{}
%\begin{document}
%\maketitle

\tableofcontents
\C

\chapter{Overview}
 \section{Introduction}
 NZMATH\cite{NZMATH} is a number theory oriented calculation system 
mainly developed by the Nakamula laboratory at Tokyo Metropolitan University.
 NZMATH system provides you mathematical, especially number-theoretic computational power.
 It is freely available and distributed under the BSD license.
The most distinctive feature of NZMATH is that it is written entirely 
using a scripting language called Python.

If you want to learn how to start using NZMATH, see Installation(section \ref{installation}) and Tutorial(section \ref{tutorial}).
 \subsection{Philosophy -- Advantages over Other Systems}
 In this section, we discuss philosophy of NZMATH, that is, the advantages of 
NZMATH compared to other similar systems.
%
\subsubsection{Open Source Software}
%
Computational algebra systems, such as Maple\cite{Maple}, 
Mathematica\cite{Mathematica}, and Magma\cite{Magma} are fare-paying systems.
These non-free systems are not distributed with source codes.
In this regard, users cannot modify such systems.
It narrows these system's potentials for users not to take part in developing it.
NZMATH, on the other hand, is an open-source software and the source code is 
openly available.
Furthermore, NZMATH is distributed under the BSD license.
BSD license claims as-is and redistribution or commercial use are permitted 
provided that these packages retain the copyright notice.
%Users can use NZMATH as they like.
%
\subsubsection{Speed of Development}
%
We took over developing of SIMATH\cite{SIMATH}, 
which was developed under the leadership of Prof.Zimmer at Saarlandes University 
in Germany.
However, it costs a lot of time and efforts to develop these system.
Almost all systems including SIMATH are implemented in C or C++ for execution speed,
but we have to take the time to work memory management, 
construction of an interactive interpreter, preparation for multiple precision package 
and so on.
In this regard, we chose Python which is a modern programming language.
Python provides automatic memory management, a sophisticated interpreter 
and many useful packages.
We can concentrate on development of mathematical matters by using Python.
%So Python enables us to concentrate on development of mathematical matters.
%
\subsubsection{Bridging the Gap between Users and Developers}
%
KANT/KASH\cite{KANT} and PARI/GP\cite{PARI} are similar systems to NZMATH.
But these systems have different languages for users and developers.
We think the gap between languages makes evolution of systems slow.
NZMATH is being developed with using Python, we bridge this gap. 
Users are easy to understand Python grammar and read codes written by Python.
And NZMATH which is one of Python libraries works on very wide platform 
including UNIX/Linux, Macintosh, Windows, and so forth.
Users can modify the programs and feedback to developers.
Developers can absorb their thinking.
Then NZMATH will progress to more flexible user-friendly system.
%
\subsubsection{Link with Other Softwares}
%
NZMATH distributed as a Python library enables us to link other Python packages with it.
For example, NZMATH can use with IPython\cite{IPython} 
which is a comfortable interactive interpreter.
And it can be linked with matplotlib\cite{matplotlib} 
which is a powerful graphic software.
There are many libraries and packages for softwares implemented in Python.
Many of these packages are freely available.
Users can use NZMATH with these packages and create an unthinkable powerful system.
%
\subsection{Information}
  NZMATH has more than 25 modules.
It has modules related with elementary number theory, combinatorial theory, solving equations, 
primality, factorization, multiplicative number theoretic functions, 
matrix, vector, polynomial, rational field, finite field, elliptic curve, and so on.
NZMATH manual for users is at:
\begin{verbatim}
http://tnt.math.metro-u.ac.jp/nzmath/manual/
\end{verbatim}
If you are interested in NZMATH, please visit the official website 
below to get more information about it.
\begin{verbatim}
http://tnt.math.metro-u.ac.jp/nzmath/
\end{verbatim}
Note that NZMATH can be used even if user do not have experience 
writing programs in Python.
%
\subsection{Installation}\label{installation}
In this section, we explain how to install NZMATH.
If your operating system (OS) is windows, then see \ref{windows install} Install for Windows Users.
\subsubsection{Basic Installation}
There are three steps for installation of NZMATH.

%First, make preparation of computer with the Python installed.
First, check that Python is installed in the computer.
Python 2.5 or a higher version is needed for NZMATH.
If you do not have a copy of Python, please install it first.
Python is available from \verb+http://www.python.org/+.

Second, download NZMATH package and expand it.
It is distributed at official web site:
\begin{verbatim}
http://tnt.math.metro-u.ac.jp/nzmath/download
\end{verbatim}
or at sourceforge.net:
\begin{verbatim}
http://sourceforge.net/project/showfiles.php?group_id=171032
\end{verbatim}
The package can be easily extracted, depending on the operating system.
For systems with recent GNU tar, type a single command below:
\begin{verbatim}
    % tar xf NZMATH-*.*.*.tar.gz
\end{verbatim}
where, \verb|%| is a command line prompt. 
With standard tar, type 
\begin{verbatim}
    % gzip -cd NZMATH-*.*.*.tar.gz | tar xf -
\end{verbatim}.
Please read *.*.* as the version number of which you downloaded the package.
For example, if the latest version is 1.0.0, then type the following command.
\begin{verbatim}
    % tar xf NZMATH-1.0.0.tar.gz
\end{verbatim}
Then, a subdirectory named NZMATH-*.*.* is created.

Finally, install NZMATH to the standard python path.
Usually, this translates to writing files somewhere 
under \verb+/usr/lib+ or \verb+/usr/local/lib+, 
and thus appropriate write permission is required.
Typically, type commands below:
\begin{verbatim}
    % cd NZMATH-*.*.*
    % su
    # python setup.py install
\end{verbatim}

\subsubsection{Installation for Windows Users}\label{windows install}
We also distribute the installation packages for specific platforms.
Especially, we started distributing installer for Windows in 2007.

Please download an installer(NZMATH-*.*.*.win32Install.exe) from
\begin{verbatim}
http://tnt.math.metro-u.ac.jp/nzmath/download
\end{verbatim}
or at sourceforge.net:
\begin{verbatim}
http://sourceforge.net/project/showfiles.php?group_id=171032
\end{verbatim}

Please open the installer.
If you use Windows Vista or higher version, UAC asks if you run the program. click "Allow".
Then the setup window will open.
Following the steps in the setup wizard can install NZMATH with only three clicks.
%
  \subsection{Tutorial}\label{tutorial}
  In this section, we describe how to use NZMATH.
  \subsubsection{Sample Session}
  Start your Python interpriter.
  That is, open your command interpriter such as Finder for MacOS or bash/csh for linux, type the strings ``python'' and press the key Enter.
\begin{ex}
% python
Python 2.6.1 (r261:67515, Jan 14 2009, 10:59:13)
[GCC 4.1.2 20071124 (Red Hat 4.1.2-42)] on linux2
Type "help", "copyright", "credits" or "license" for more information.
>>>
\end{ex}
  For windows users, it normally means open IDLE (Python GUI), which is a Python software. 
\begin{ex}
Python 2.6.1 (r261:67517, Dec  4 2008, 16:51:00) [MSC v.1500 32 bit (Intel)] on win32
Type "copyright", "credits" or "license()" for more information.

    ****************************************************************
    Personal firewall software may warn about the connection IDLE
    makes to its subprocess using this computer's internal loopback
    interface.  This connection is not visible on any external
    interface and no data is sent to or received from the Internet.
    ****************************************************************
    
IDLE 2.6.1      
>>> 
\end{ex}
Here, '\verb+>>>+' is a Python prompt, which means that system waits you to input commands.

Then, type:
\begin{ex}
>>> from nzmath import *
>>>
\end{ex}
You are ready to use NZMATH package.
For example, type the string ``prime.nextPrime(1000)'', then you will obtain `1009'' as the smallest prime among numbers greater than $1000$.
\begin{ex}
>>> prime.nextPrime(1000)
1009
>>>
\end{ex}
``prime'' is a name of a module, which is a NZMATH file including Python codes.
``nextPrime'' is a name of a function, which outputs values after executing some process for inputs.
NZMATH has various functions for mathematical or algorithmical computations.
See \ref{function} Functions.

Also, we can create some mathematical objects.
For example, you may use the module ``matrix'' as the following.
\begin{ex}
>>> A = matrix.Matrix(2, 2, [1, 2]+[5, 6])
>>> print A
1 2
5 6
>>> print A ** 2
11 14
35 46
>>>
\end{ex}
``Matrix'' is a name of a class, which is a template of mathematical objects.
See \ref{class} Classes for using NZMATH classes.

The command ``print'' enables us to represent outputs with good-looking forms.
The data structure ``[a, b, c, $\cdots$]'' is called list.
Also, we use various Python data structures like tuple ``(a, b, c, $\cdots$)'', dictionary ``$\{x_1:y_1, x_2:y_2, x_3:y_3, \cdots\}$'' etc.
These follow syntax of Python programming language.
We do not explain Python's syntax in detail because it is not absolutely necessary to use NZMATH.
However, we recommend that you learn Python for development of your potential.
You are easy to study Python grammers.
For instance, see \verb+http://docs.python.org+.
  
 % \subsection{Python $\&$ NZMATH}
 %  \subsubsection{Save to a file}
 \subsection{Note on the Document}
   \paragraph{$\dagger$}
   The sections, sentences and words, which is marked $\dagger$, are documents for advanced users.
   For example, the class \textit{FiniteFieldElement} (See \ref{}) is one of the abstract classes in NZMATH, which can be used for making new classes similar to the finite field.
   \paragraph{[$\cdots$]}
   For example, we may sometimes write as \textit{function(a,b[,c,d])} and this means the argument ``c, d'' or only ``d'' can be discarded.
   This function uses``default argument values'', which is one of the feature of Python (See [default augment values]).
   
   \textbf{Warning}:\ Python also have the feature ``keyword arguments''.
   We have tried to keep the feature in NZMATH too,
   but some modules could rearrange arguments
   depending not on keywords but on the place where one do not give arguments. 
%

\chapter{Basic Utilities}\label{utility}
 %%--<config>--%%
 %%--<bigrandom>--%%
 %%--<bigrange>--%%
 %%--<compatibility>--%%
%
\chapter{Functions}\label{function}
 %%--<arith1>--%%
 %%--<arygcd>--%%
 %%--<combinatorial>--%%
 %%--<cubic_root>--%%
 %%--<ecpp>--%%
 %%--<equation>--%%
 %%--<gcd>--%%
 %%--<multiplicative>--%%
 %%--<prime>--%%
 %%--<quad>--%%
 %%--<round2>--%%
 %%--<squarefree>--%%
 %%--<zassenhaus>--%%
%
\chapter{Classes}\label{class}
 %%--<algfield>--%%
 %%--<elliptic>--%%
 %%--<finitefield>--%%
 %%--<group>--%%
 %%--<imaginary>--%%
 %%--<intresidue>--%%
 %%--<lattice>--%%
 %%--<matrix>--%%
 %%--<permute>--%%
 %%--<polynomial>--%%
 %%--<rational>--%%
 %%--<real>--%%
 %%--<ring>--%%
 %%--<vector>--%%
 %%--<factor.ecm>--%%
 %%--<factor.find>--%%
 %%--<factor.methods>--%%
 %%--<factor.misc>--%%
 %%--<factor.mpqs>--%%
 %%--<factor.util>--%%
 %%--<poly.factor>--%%
 %%--<poly.formalsum>--%%
 %%--<poly.hensel>--%%
 %%--<poly.multiutil>--%%
 %%--<poly.multivar>--%%
 %%--<poly.ratfunc>--%%
 %%--<poly.ring>--%%
 %%--<poly.termorder>--%%
 %%--<poly.uniutil>--%%
 %%--<poly.univar>--%%
 
\bibliographystyle{jplain}%use jbibtex
\bibliography{nzmath_references}

\end{document}
