\documentclass{report}

\input{../header_basic_util}

%---------- start document ---------- %
 \section{config -- setting features}\linkedzero{config}
%
All constants in the module can be set in user's config file.
See the~\hyperlink{config.user}{User Settings} section for
more detailed description.

  \subsection{Default Settings}\linkedone{config}{default}

  \subsubsection{Dependencies}\linkedone{config}{dependencies}

  Some third party / platform dependent modules are possibly used, and
  they are configurable.

  \paragraph{HAVE\_MPMATH}\linkedone{config}{HAVE\_MPMATH}

  {\tt mpmath} is a package providing multiprecision math.
  See its \href{http://code.google.com/p/mpmath}{project page}.
  This package is used in \linkingzero{ecpp} module.

  \paragraph{HAVE\_SQLITE3}\linkedone{config}{HAVE\_SQLITE3}

  {\tt sqlite3} is the default database module for \python,
  but it need to be enabled at the build time.

  \paragraph{HAVE\_NET}\linkedone{config}{HAVE_NET}

  Some functions will connect to the Net.
  Desktop machines are usually connected to the Net, but notebooks may
  have connectivity only occasionally.

  \subsubsection{Plug-ins}\linkedone{config}{Plug-ins}

  \paragraph{PLUGIN\_MATH}\linkedone{config}{PLUGIN\_MATH}
  \python standard float/complex types and \linklibrary{math}/\linklibrary{cmath} modules only
  provide fixed precision (double precision), but sometimes
  multiprecision floating point is needed.

  \subsubsection{Assumptions}\linkedone{config}{assumptions}

  Some conjectures are useful for assuring the validity of a faster
  algorithm.

  All assumptions are default to {\tt False}, but you can set them
  {\tt True} if you believe them.

  \paragraph{GRH}\linkedone{config}{GRH}

  Generalized Riemann Hypothesis.  For example, primality test is
  \(O((\log n)^2)\) if GRH is true while \(O((\log n)^6)\) or something
  without it.

  \subsubsection{Files}\linkedone{config}{files}

  \paragraph{DATADIR}\linkedone{config}{DATADIR}

  The directory where \nzmath (static) data files are stored. The
  default will be {\tt os.path.join(sys.prefix, 'share', 'nzmath')} or
  {\tt os.path.join(sys.prefix, 'Data', 'nzmath')} on Windows.

  \subsection{Automatic Configuration}\linkedone{config}{auto}

  The items above can be set automatically by testing the environment.

  \subsubsection{Checks}\linkedone{config}{checks}

  Here are check functions.

  The constants accompanying the check functions which enable the check
  if it is {\tt True}, can be overridden in user settings.

  Both check functions and constants are not exposed.

  \paragraph{check\_mpmath()}\linkedone{config}{check\_mpmath}

  Check whether {\tt mpmath} is available or not.

  constant: {\tt CHECK\_MPMATH}

  \paragraph{check\_sqlite3()}\linkedone{config}{check\_sqlite3}

  Check if {\tt sqlite3} is importable or not.
  {\tt pysqlite2} may be a substitution.

  constant: {\tt CHECK\_SQLITE3}

  \paragraph{check\_net()}\linkedone{config}{check\_net}

  Check the net connection by HTTP call.

  constant: {\tt CHECK\_NET}

  \paragraph{check\_plugin\_math()}\linkedone{config}{check\_plugin\_math}

  Check which math plug-in is available.

  constant: {\tt CHECK\_PLUGIN\_MATH}

  \paragraph{default\_datadir()}\linkedone{config}{default\_datadir}

  Return default value for {\tt DATADIR}.

  This function selects the value from various candidates.
  If this function is called with {\tt DATADIR} set, the value of (previously-defined) {\tt DATADIR} is the first candidate to be returned. Other
  possibilities are, {\tt sys.prefix + 'Data/nzmath'} on Windows, or
  {\tt sys.prefix + 'share/nzmath'} on other platforms.

  Be careful that all the above paths do not exist, the function
  returns {\tt None}.

  constant: {\tt CHECK\_DATADIR}

  \subsection{User Settings}\linkedone{config}{user}

  The module try to load the user's config file named
  {\it nzmathconf.py}. The search path is the following:
  \begin{enumerate}
  \item The directory which is specified by an environment variable
    {\tt NZMATHCONFDIR}.
  \item If the platform is Windows, then
    \begin{enumerate}
    \item If an environment variable {\tt APPDATA} is set, {\tt
        APPDATA/nzmath}.
    \item If, alternatively, an environment variable {\tt USERPROFILE}
      is set,\linebreak {\tt USERPROFILE/Application~Data/nzmath}.
    \end{enumerate}
  \item On other platforms, if an environment variable {\tt HOME} is
    set, {\tt HOME/.nzmath.d}.
  \end{enumerate}

  {\it nzmathconf.py} is a \python script. Users can set the constants
  like {\tt HAVE\_MPMATH}, which will override the default settings. These
  constants, except assumption ones, are automatically set, unless
  constants accompanying the check functions are false (see 
  the~\hyperlink{config.auto}{Automatic Configuration} section above).

%---------- end document ---------- %

\input{../footer}
