\input{../header_function}

%---------- start document ---------- %
 \section{factor.ecm -- ECM factorization}\linkedzero{factor.ecm}

 This module has curve type constants:
 \begin{description}\linkedone{factor.ecm}{curvetype}
   \item[S]\linkedone{factor.ecm}{S}: aka SUYAMA. Suyama's parameter selection strategy.
   \item[B]\linkedone{factor.ecm}{B}: aka BERNSTEIN. Bernstein's parameter selection strategy.
   \item[A1]\linkedone{factor.ecm}{A1}: aka ASUNCION1. Asuncion's parameter selection strategy variant 1.
   \item[A2]\linkedone{factor.ecm}{A2}: aka ASUNCION2.  ditto 2.
   \item[A3]\linkedone{factor.ecm}{A3}: aka ASUNCION3.  ditto 3.
   \item[A4]\linkedone{factor.ecm}{A4}: aka ASUNCION4.  ditto 4.
   \item[A5]\linkedone{factor.ecm}{A5}: aka ASUNCION5.  ditto 5.
 \end{description}
 See J.S.Asuncion's master thesis~\cite{Janice} for details of each family.

%
  \subsection{ecm -- elliptic curve method}\linkedone{factor.ecm}{ecm}
   \func{ecm}
   {%
     \hiki{n}{integer},\ %
     \hikiopt{curve\_type}{\linkingone{factor.ecm}{curvetype}}{A1},\ %
     \hikiopt{incs}{integer}{3},\ %
     \hikiopt{trials}{integer}{20},\ %
     \hikiopt{verbose}{bool}{False}%
   }{%
     \out{integer}
   }\\
   \spacing
   % document of basic document
   \quad Find a factor of \param{n} by elliptic curve method.\\
   \spacing
   % added document
   If it cannot find non-trivial factor of $n$, then it returns $1$.\\ 
   \spacing
   % input, output document
   \quad \param{curve\_type} should be chosen from \linkingone{factor.ecm}{curvetype} constants above.\\
   \quad The second optional argument \param{incs} specifies a number
   of changes of bounds. The function repeats factorization
   trials several times changing curves with a fixed bounds.\\
   \quad Optional argument \param{trials} can control how quickly move
   on to the next higher bounds.\\
   \quad \param{verbose} toggles verbosity.\\
\C

%---------- end document ---------- %

\input{../footer}
