\documentclass{report}

\input{../header_class}

%---------- start document ---------- %
 \section{poly.ratfunc -- rational function}\linkedzero{poly.ratfunc}
 \begin{itemize}
   \item {\bf Classes}
   \begin{itemize}
     \item \linkingone{poly.ratfunc}{RationalFunction}
   \end{itemize}
 \end{itemize}

 A rational function is a ratio of two polynomials.

 Please don't expect this module is useful.
 It just provides an acceptable container for polynomial division.
\C

 \subsection{RationalFunction -- rational function class}\linkedone{poly.ratfunc}{RationalFunction}
 \initialize
  \func{RationalFunction}{\hiki{numerator}{polynomial},\ \hikiopt{denominator}{polynomial}{1}}{\out{RationalFunction}}\\
  \spacing
  % document of basic document
  \quad Make a rational function with the given \param{numerator} and
  \param{denominator}.
  % added document
  %
  % \spacing
  % input, output document
  If the \param{numerator} is a {\tt RationalFunction} instance and
  \param{denominator} is not given, then make a copy.
  If the \param{numerator} is a kind of polynomial, then make a rational
  function whose numerator is the given polynomial.
  Additionally, if \param{denominator} is also given,
  the denominator is set to its values, otherwise the denominator is 1.
  \begin{at}
    \item[numerator]\linkedtwo{poly.ratfunc}{RationalFunction}{numerator}:\\
      polynomial.
    \item[denominator]\linkedtwo{poly.ratfunc}{RationalFunction}{denominator}:\\
      polynomial.
  \end{at}
  \begin{op}
    \verb+A==B+ & Return whether {\tt A} and {\tt B} are equal or not.\\
    \verb+str(A)+ & Return readable string.\\
    \verb+repr(A)+ & Return string representing {\tt A}'s structure.\\
  \end{op}
  \method
  \subsubsection{getRing -- get rational function field}\linkedtwo{poly.ratfunc}{RationalFunction}{getRing}
   \func{getRing}{\param{self}}{\linkingone{poly.ring}{RationalFunctionField}}\\
   \spacing
   % document of basic document
   \quad Return the rational function field to which the rational function belongs.
\C

%---------- end document ---------- %

\input{../footer}
