\documentclass{report}

\input{header_function}

%---------- start document ---------- %
 \section{bigrandom -- random numbers}\linkedzero{bigrandom}
%
 \paragraph{Historical Note}\label{bigrandom_historical_note}

 The module was written for replacement of the \python standard module
 \linklibrary{random}, because in the era of \python 2.2 (prehistorical period of
 \nzmath) the random module raises {\tt OverflowError} for long integer
 arguments for the \linklibraryone{random\#random.randrange}{randrange} function, which is the only function
 having a use case in \nzmath.

 After the creation of \python 2.3, it was theoretically possible to
 use {\tt random.randrange}, since it started to accept long integer
 as its argument. Use of it was, however, not considered, since there
 had been the {\tt bigrandom} module. It was lucky for us. In fall of
 2006, we found a bug in {\tt random.randrange} and reported it (see
 issue tracker); the {\tt random.randrange} accepts long integers but
 returns unreliable result for truly big integers. The bug was fixed
 for \python 2.5.1. You can, therefore, use {\tt random.randrange}
 instead of {\tt bigrandom.randrange} for \python 2.5.1 or higher.

  \subsection{random -- random number generator}\linkedone{bigrandom}{random}
   \func{random}
   {}{{\em float}}\\
   \spacing
   % document of basic document
   \quad Return a random floating point number in the interval \([0, 1)\).\\
   \spacing
   % added document
   \quad This function is an alias to {\tt random.random} in the \python standard library.\\
   % input, output document
%
  \subsection{randrange -- random integer generator}\linkedone{bigrandom}{randrange}
   \func{randrange}
   {%
     \hiki{start}{integer},\ %
     \hikiopt{stop}{integer}{None},\ %
     \hikiopt{step}{integer}{1}
   }{%
     {\em integer}
   }\\
   \spacing
   % document of basic document
   \quad Return a random integer in the range.\\
   \spacing
   % input, output document
   \quad The argument names do not correspond to their roles, but
   users are familiar with the
   \linklibraryone{functions\#range}{range} built-in function of
   \python and understand the semantics.  Calling with one argument
   \(n\), then the result is an integer in the range \([0, n)\) chosen
   randomly.  With two arguments \(n\) and \(m\),
   in \([n, m)\), and with third \(l\), in \([n, m) \cap (n + l\mathbb{Z})\).\\
   \spacing \quad This function is almost the same as {\tt
     random.randrange} in the \python standard library.  See the
   historical note~\ref{bigrandom_historical_note}.
%
\begin{ex}
>>> randrange(4, 10000, 3)
9919L
>>> randrange(4 * 10**60)
31925916908162253969182327491823596145612834799876775114620151L
\end{ex}%Don't indent!(indent causes an error.)

   \subsection{map\_choice -- choice from image of mapping}\linkedone{bigrandom}{map\_choice}
   \func{map\_choice}
   {%
     \hiki{mapping}{function},\ %
     \hiki{upperbound}{integer}
   }{%
     {\em integer}
   }\\
   \spacing
   \quad Return a choice from a set given as the image of the mapping
   from natural numbers (more precisely {\tt range(upperbound)}).  In
   other words, it is equivalent to:
   {\tt random.\linklibraryone{random\#choice}{choice}([mapping(i) for i in range(upperbound)])},
   if \param{upperbound} is small enough for the list size limit.\\
   \spacing
   \quad The \param{mapping} can be a partial function, i.e. it may return
   {\tt None} for some input. However, if the resulting set is empty, it
   will end up with an infinite loop.\\
\C

%---------- end document ---------- %

\input{footer}
