\documentclass{report}

\input{../header_function}

%---------- start document ---------- %
 \section{combinatorial -- combinatorial functions}\linkedzero{combinatorial}
%
  \subsection{binomial -- binomial coefficient}\linkedone{combinatorial}{binomial}
   \func{binomial}
   {%
     \hiki{n}{integer},\ %
     \hiki{m}{integer}
   }{%
     \out{integer}
   }\\
   \spacing
   % document of basic document
   \quad \param{n}と\param{m}の二項係数の値を返す。
   すなはち、 $\displaystyle{\frac{\param{n} !}{(\param{n} - \param{m}) ! \param{m} !}}$.\\
   \spacing
   % added document
   \negok 便宜上、{\tt binomial(n, n+i)}は\(0\)整数\(i\)に対して\(0\)を返し、 {\tt binomial(0,0)}は\(1\)を返す。\\
   \spacing
   % input, output document
   \quad \param{n}は自然数。 \param{m}は整数。 \\

  \subsection{combinationIndexGenerator -- iterator for combinations}\linkedone{combinatorial}{combinationIndexGenerator}

   \func{combinationIndexGenerator}{%
     \hiki{n}{integer},\ %
     \hiki{m}{integer}
   }{%
     \out{iterator}
   }\\
   \spacing
   % document of basic document
   \quad Return an iterator which generates indices of \param{m}
   element subsets of \param{n} element set.\\
   \spacing 
   \quad {\tt combination\_index\_generator}\linkedone{combinatorial}{combination\_index\_generator}
   is an alias of {\tt combinationIndexGenerator}.\\

  \subsection{factorial -- factorial}\linkedone{combinatorial}{factorial}
   \func{factorial}{%
     \hiki{n}{integer}
   }{%
     \out{integer}
   }\\
   \spacing
   % document of basic document
   \quad \(\param{n}!\) の値を返す。\param{n}は整数。\\

  \subsection{permutationGenerator -- iterator for permutation}\linkedone{combinatorial}{permutationGenerator}
  \func{permutationGenerator}{%
    \hiki{n}{integer}
  }{%
    \out{iterator}
  }
   \spacing
   \quad Generate all permutations of \param{n} elements as list iterator.\\
   % 
   \spacing 
   \quad The number of generated list is \param{n}'s
   \linkingone{combinatorial}{factorial}, so be careful to use
   big \param{n}.\\
   \spacing 
   \quad {\tt permutation\_generator}\linkedone{combinatorial}{permutation\_generator}
   is an alias of {\tt permutationGenerator}.\\

  \subsection{fallingfactorial -- the falling factorial}\linkedone{combinatorial}{fallingfactorial}
   \func{fallingfactorial}{%
     \hiki{n}{integer},\ %
     \hiki{m}{integer}
   }{%
     \out{integer}
   }\\
   \spacing
   % document of basic document
   \quad 下降階乗の値を返す。; \param{n}から\param{m}へ。
   i.e. \(n(n-1)\cdots(n-m+1)\).\\

  \subsection{risingfactorial -- the rising factorial}\linkedone{combinatorial}{risingfactorial}
   \func{risingfactorial}{%
     \hiki{n}{integer},\ %
     \hiki{m}{integer}
   }{%
     \out{integer}
   }\\
   \spacing
   % document of basic document
   \quad　上昇階乗の値を返す。; \param{n}から\param{m}へ。
   i.e.\, \(n(n+1)\cdots(n+m-1)\).\\

  \subsection{multinomial -- the multinomial coefficient}\linkedone{combinatorial}{multinomial}
   \func{multinomial}{%
     \hiki{n}{integer},\ %
     \hiki{parts}{list}
   }{%
     \out{integer}
   }\\
   \spacing
   % document of basic document
   \quad 多項係数の値を返す。\\
   \spacing
   % input, output document
   \quad \param{parts}は自然数数列。\param{parts}の要素をすべてあわせると\param{n}と等しくなる。\\

  \subsection{bernoulli -- the Bernoulli number}\linkedone{combinatorial}{bernoulli}
   \func{bernoulli}{%
     \hiki{n}{integer}
   }{%
     \out{Rational}
   }\\
   \spacing
   % document of basic document
   \quad　\param{n}次Bernoulli数の値を返す。\\

  \subsection{catalan -- the Catalan number}\linkedone{combinatorial}{catalan}
   \func{catalan}{%
     \hiki{n}{integer}
   }{%
     \out{integer}
   }\\
   \spacing
   % document of basic document
   \quad \param{n}次Catalan数の値を返す。\\

  \subsection{euler -- the Euler number}\linkedone{combinatorial}{euler}
   \func{euler}{%
     \hiki{n}{integer}
   }{%
     \out{integer}
   }\\
   \spacing
   % document of basic document
   \quad \param{n}次Euler数の値を返す。\\

  \subsection{bell -- the Bell number}\linkedone{combinatorial}{bell}
   \func{bell}{%
     \hiki{n}{integer}
   }{%
     \out{integer}
   }\\
   \spacing
   % document of basic document
   \quad \param{n}次ベル数の値を返す。.\\
   \spacing
   % added document
   \quad ベル数 \(b\)の定義:
   \[b(n) = \sum_{i=0}^{n} S(n, i),\ \]
   \(S\)は第２種スターリング数。(\linkingone{combinatorial}{stirling2}).\\

  \subsection{stirling1 -- Stirling number of the first kind}\linkedone{combinatorial}{stirling1}
   \func{stirling1}{%
     \hiki{n}{integer},\ %
     \hiki{m}{integer}
   }{%
     \out{integer}
   }\\
   \spacing
   % document of basic document
   \quad 第１種スターリング数の値を返す。\\
   \spacing
   % added document
   \quad　\(s\)はスターリング数。\((x)_n\)は下降階乗。
   \[(x)_n = \sum_{i=0}^{n} s(n,\ i) x^i. \]\\
   \(s\) satisfies the recurrence relation:
   \[s(n,\ m) = s(n-1,\ m-1) - (n-1)s(n-1,\ m)\ .\]\\

  \subsection{stirling2 -- Stirling number of the second kind}\linkedone{combinatorial}{stirling2}
   \func{stirling2}{%
     \hiki{n}{integer},\ %
     \hiki{m}{integer}
   }{%
     \out{integer}
   }\\
   \spacing
   % document of basic document
   \quad Return Stirling number of the second kind.\\
   \spacing
   % added document
   \quad \(S\)はスターリング数。 \((x)_i\)は下降階乗。:
   \[x^n = \sum_{i=0}^{n} S(n,\ i) (x)_i\]
   \(S\)は以下の関係を充たす。
   \[S(n,\ m) = S(n-1,\ m-1) + m S(n-1,\ m)\]\\

  \subsection{partition\_number -- the number of partitions}\linkedone{combinatorial}{partition\_number}
   \func{partition\_number}{%
     \hiki{n}{integer}
   }{%
     \out{integer}
   }\\
   \spacing
   % document of basic document
   \quad \param{n}の分割数の値を返す。\\

  \subsection{partitionGenerator -- iterator for partition}\linkedone{combinatorial}{partitionGenerator}
   \func{partitionGenerator}{%
     \hiki{n}{integer},\ %
     \hikiopt{maxi}{integer}{0}
   }{%
     \out{iterator}
   }\\
   \spacing
   % document of basic document
   \quad Return an iterator which generates partitions of \param{n}.\\
   % input, output document
   \spacing
   \quad If \param{maxi} is given, then summands are limited not to exceed \param{maxi}.\\
   \quad The number of partitions (given by
   \linkingone{combinatorial}{partition\_number}) grows exponentially,
   so be careful to use big \param{n}.\\
   \spacing 
   \quad {\tt partition\_generator}\linkedone{combinatorial}{partition\_generator}
   is an alias of {\tt partitionGenerator}.\\

  \subsection{partition\_conjugate -- the conjugate of partition}\linkedone{combinatorial}{partition\_conjugate}
   \func{partition\_conjugate}{%
     \hiki{partition}{tuple}
   }{%
     \out{tuple}
   }\\
   \spacing
   % document of basic document
   \quad Return the conjugate of \param{partition}.\\

\begin{ex}
>>> combinatorial.binomial(5, 2)
10L
>>> combinatorial.factorial(3)
6L
>>> combinatorial.fallingfactorial(7, 3) == 7 * 6 * 5
True
>>> combinatorial.risingfactorial(7, 3) == 7 * 8 * 9
True
>>> combinatorial.multinomial(7, [2, 2, 3])
210L
>>> for idx in combinatorial.combinationIndexGenerator(5, 3):
...     print idx
...
[0, 1, 2]
[0, 1, 3]
[0, 1, 4]
[0, 2, 3]
[0, 2, 4]
[0, 3, 4]
[1, 2, 3]
[1, 2, 4]
[1, 3, 4]
[2, 3, 4]
>>> for part in combinatorial.partitionGenerator(5):
...     print part
...
(5,)
(4, 1)
(3, 2)
(3, 1, 1)
(2, 2, 1)
(2, 1, 1, 1)
(1, 1, 1, 1, 1)
>>> combinatorial.partition_number(5)
7
>>> def limited_summands(n, maxi):
...     "partition with limited number of summands"
...     for part in combinatorial.partitionGenerator(n, maxi):
...         yield combinatorial.partition_conjugate(part)
...
>>> for part in limited_summands(5, 3):
...     print part
...
(2, 2, 1)
(3, 1, 1)
(3, 2)
(4, 1)
(5,)
\end{ex}%Don't indent!(indent causes an error.)

\C

%---------- end document ---------- %

\input{../footer}
