\documentclass{report}

\input{../header_function}

%---------- start document ---------- %
 \section{ecpp -- elliptic curve primality proving}\linkedzero{ecpp}
 The module consists of various functions for ECPP (Elliptic Curve Primality Proving).

 It is probable that the module will be refactored in the future so that each function be placed in other modules.\\
\spacing
The ecpp module requires mpmath.

%
  \subsection{ecpp -- elliptic curve primality proving}\linkedone{ecpp}{ecpp}
   \func{ecpp}
   {%
     \hiki{n}{integer},\ %
     \hikiopt{era}{list}{None}%
   }{%
     \out{bool}%
   }\\
   \spacing
   % document of basic document
   \quad Do elliptic curve primality proving.\\
   If \param{n} is prime, return True. Otherwise, return False. \\
   \spacing
   % added document
   The optional argument \param{era} is a list of primes (which stands for ERAtosthenes).\\
   \spacing
   % input, output document
   \quad \param{n} must be a big integer.\\
%
  \subsection{hilbert -- Hilbert class polynomial}\linkedone{ecpp}{hilbert}
   \func{hilbert}
        {\hiki{D}{integer}}
        {\out{(integer, list)}}\\
   \spacing
   % document of basic document
   \quad Return the class number and Hilbert class polynomial for the imaginary quadratic field with fundamental discriminant \param{D}.\\
   \spacing
   % added document
   \quad Note that this function returns Hilbert class polynomial as a list of coefficients.\\
   \negok If the option \linkingone{config}{HAVE\_NET} is set, at first try to retrieve the data in \url{http://hilbert-class-polynomial.appspot.com/}.
   If the data corresponding to \param{D} is not found, compute the Hilbert polynomial directly (for a long time).\\
   \spacing
   % input, output document
   \quad \param{D} must be negative int or long. See \cite{Pomerance}.\\
%
  \subsection{dedekind -- Dedekind's eta function}\linkedone{ecpp}{dedekind}
   \func{dedekind}
        {\hiki{tau}{mpmath.mpc}, \ 
         \hiki{floatpre}{integer}}
        {\out{mpmath.mpc}}\\
   \spacing
   % document of basic document
   \quad Return Dedekind's eta of a complex number \param{tau} in the upper half-plane. \\
   \spacing
   % added document
   \quad Additional argument \param{floatpre} specifies the precision of calculation in decimal digits.\\
   \spacing
   % input, output document
   \quad \param{floatpre} must be positive int. \\
%
  \subsection{cmm -- CM method}\linkedone{ecpp}{cmm}
   \func{cmm}
        {\hiki{p}{integer}}
        {\out{list}}\\
   \spacing
   % document of basic document
   \quad Return curve parameters for CM curves.\\
   \spacing
   % added document
   \quad If you also need its orders, use \linkingone{ecpp}{cmm\_order}.\\
   \spacing
   % input, output document
   \quad A prime \param{p} has to be odd.\\
   This function returns a list of (\param{a},\ \param{b}), where (\param{a},\ \param{b}) expresses Weierstrass' short form.
%
  \subsection{cmm\_order -- CM method with order}\linkedone{ecpp}{cmm\_order}
   \func{cmm\_order}
        {\hiki{p}{integer}}
        {\out{list}}\\
   \spacing
   % document of basic document
   \quad Return curve parameters for CM curves and its orders.\\
   \spacing
   % added document
   \quad If you need only curves, use \linkingone{ecpp}{cmm}.\\
   \spacing
   % input, output document
   \quad A prime \param{p} has to be odd.\\
   This function returns a list of (\param{a},\ \param{b},\ \param{order}), where (\param{a},\ \param{b}) expresses Weierstrass' short form and \param{order} is the order of the curve.
%
  \subsection{cornacchiamodify -- Modified cornacchia algorithm}\linkedone{ecpp}{cornacchiamodify}
   \func{cornacchiamodify}
        {\hiki{d}{integer},\ 
        \hiki{p}{integer}}
        {\out{list}}\\
   \spacing
   % document of basic document
   \quad Return the solution $(u,\ v)$ of $u^2 - \param{d}v^2 = 4\param{p}$.\\
   \spacing
   % added document
   \quad If there is no solution, raise ValueError.\\
   \spacing
   % input, output document
   \quad  \param{p} must be a prime integer and \param{d} be an integer such that $\param{d} < 0$ and $\param{d} > -4\param{p}$ with $\param{d} \equiv 0, 1 \pmod{4}$.\\
%
\begin{ex}
>>> ecpp.ecpp(300000000000000000053)
True
>>> ecpp.hilbert(-7)
(1, [3375, 1])
>>> ecpp.cmm(7)
[(6L, 3L), (5L, 4L)]
>>> ecpp.cornacchiamodify(-7, 29)
(2, 4)
\end{ex}%Don't indent!(indent causes an error.)
\C

%---------- end document ---------- %

\input{../footer}
