\documentclass{report}

\input{../header_function}

%---------- start document ---------- %
 \section{equation -- solving equations, congruences }\linkedzero{equation}

 In the following descriptions, some type aliases are used.
 \begin{description}
   \item[poly\_list]\linkedone{equation}{poly\_list}:\\
     \param{poly\_list} is a list {\tt [a0, a1, \ldots, an]}
     representing a polynomial coefficients in ascending order, i.e.,
     meaning \(a_0 + a_1 X + \cdots + a_n X^n\).  The type of each
     {\tt ai} depends on each function (explained in their descriptions).

   \item[integer]\linkedone{equation}{integer}:\\
     \param{integer} is one of {\it int}, {\it long} or \linkingone{rational}{Integer}.
   \item[complex]\linkedone{equation}{complex}:\\
     \param{complex} includes all number types in the complex field:
     \linkingone{equation}{integer}, {\it float}, {\it complex} of \python,
     \linkingone{rational}{Rational} of \nzmath, etc.\\
 \end{description}
%
  \subsection{e1 -- solve equation with degree 1}\linkedone{equation}{e1}
   \func{e1}{\hiki{f}{\linkingone{equation}{poly\_list}}}{\out{\linkingone{equation}{complex}}}\\
   \spacing
   % document of basic document
   \quad $ax + b = 0$の値を返す。\\
   \spacing
   % added document
   %\spacing
   % input, output document
   \quad \param{f}は\linkingone{equation}{complex}のlinkingone{equation}{poly\_list} {\tt [b, a]}でなければならない。\\
%
  \subsection{e1\_ZnZ -- solve congruent equation modulo n with degree 1}\linkedone{equation}{e1\_ZnZ}
   \func{e1\_ZnZ}{\hiki{f}{\linkingone{equation}{poly\_list}},\ \hiki{n}{integer}}{\out{integer}}\\
   \spacing
   % document of basic document
   \quad $ax + b  \equiv 0 \pmod{\param{n}}$.の値を返す。\\
   \spacing
   % added document
   %\spacing
   % input, output document
   \quad \param{f}は\linkingone{equation}{integer}の\linkingone{equation}{poly\_list} {\tt [b, a]}でなければならない。\\
%
  \subsection{e2 -- solve equation with degree 2}\linkedone{equation}{e2}
   \func{e2}{\hiki{f}{\linkingone{equation}{poly\_list}}}{\out{tuple}}\\
   \spacing
   % document of basic document
   \quad $ax^2 + bx + c = 0$の値を返す。\\
   \spacing
   % added document
   %\spacing
   % input, output document
   \quad \param{f}は\linkingone{equation}{complex}の\linkingone{equation}{poly\_list} {\tt [c, b, a]}でなければならない。\\
   結果のタップルは副根も含め二つの根である。\\
%
  \subsection{e2\_Fp -- solve congruent equation modulo p with degree 2}\linkedone{equation}{e2\_Fp}
   \func{e2\_Fp}{\hiki{f}{\linkingone{equation}{poly\_list}},\ \hiki{p}{integer}}{\out{list}}\\
   \spacing
   % document of basic document
   \quad $ax^2 + bx + c  \equiv 0 \pmod{\param{p}}$の値を返す。\\
   \spacing
   % added document
   \quad 同じ値が返ってきたならば、その値は多重根である。 \\
   \spacing
   % input, output document
   \quad \param{f}は \linkingone{equation}{integer}s {\tt [c, b, a]}の\linkingone{equation}{poly\_list}
　　でなければならない。
   さらに、\param{p}は素数整数。\linkingone{equation}{integer}. \\
%
  \subsection{e3 -- solve equation with degree 3}\linkedone{equation}{e3}
   \func{e3}{\hiki{f}{\linkingone{equation}{poly\_list}}}{\out{list}}\\
   \spacing
   % document of basic document
   \quad　$ax^3 + bx^2 + cx + d = 0$の値を返す。\\
   \spacing
   % added document
   %\spacing
   % input, output document
   \quad \param{f}は\linkingone{equation}{complex}の\linkingone{equation}{poly\_list} {\tt [d, c, b, a]}でなければならない。\\
   この結果のタップルには重根を含めて三つの根がある。\\
%
  \subsection{e3\_Fp -- solve congruent equation modulo p with degree 3}\linkedone{equation}{e3\_Fp}
   \func{e3\_Fp}{\hiki{f}{\linkingone{equation}{poly\_list}},\ \hiki{p}{integer}}{\out{list}}\\
   \spacing
   % document of basic document
   \quad $ax^3 + bx^2 + cx + d  \equiv 0 \pmod{\param{p}}$の値を返す。\\
   \spacing
   % added document
   \quad 同じ値が返ってきたならば、その値は多重根である。 \\
   \spacing
   % input, output document
   \quad \param{f}は\linkingone{equation}{integer}の\linkingone{equation}{poly\_list} {\tt [d, c, b, a]}でなければならない。
   In addition, \param{p}は素数整数である。\linkingone{equation}{integer}. \\
  \subsection{Newton -- solve equation using Newton's method}\linkedone{equation}{Newton}
   \func{Newton}{%
     \hiki{f}{\linkingone{equation}{poly\_list}},\ %
     \hikiopt{initial}{\linkingone{equation}{complex}}{1},\ %
     \hikiopt{repeat}{integer}{250}}{\out{complex}}\\
   \spacing
   % document of basic document
   \quad $a_nx^n + \cdots + a_1x + a_0=0$の値を返す。\\
   \spacing
   % added document
   \quad　もしすべての根を得たいのなら\linkingone{equation}{SimMethod}を使うことをお勧めする。\\
   \negok もし\param{initial}が実数根を持たない実数ならばこの関数は役に立たない。\\
   \spacing
   % input, output document
   \quad \param{f}は\linkingone{equation}{complex}の\linkingone{equation}{poly\_list}でなければならない。
   
   \param{initial} is an initial approximation \linkingone{equation}{complex} number.
   \param{repeat}は根を近似する数である。\\
%
  \subsection{SimMethod -- find all roots simultaneously}\linkedone{equation}{SimMethod}
   \func{SimMethod}{%
     \hiki{f}{\linkingone{equation}{poly\_list}},\ %
     \hikiopt{NewtonInitial}{\linkingone{equation}{complex}}{1},\ %
     \hikiopt{repeat}{integer}{250}}{\out{list}}\\
   \spacing
   % document of basic document
   \quad　$a_nx^n + \cdots + a_1x + a_0$の根の一つを返す。\\
   \spacing
   % added document
   \quad \negok もしこの方程式が多重根を持っていたら、エラーが返ってくるかもしれない。 \\
   \spacing
   % input, output document
   \quad \param{f}は\linkingone{equation}{complex}の\linkingone{equation}{poly\_list}でなければならない。
   \\
   \param{NewtonInitial}と\param{repeat}は近似値を得るため 
   \linkingone{equation}{Newton}を通過するだろう。\\
%
  \subsection{root\_Fp --  solve congruent equation modulo p}\linkedone{equation}{root\_Fp}
   \func{root\_Fp}{\hiki{f}{\linkingone{equation}{poly\_list}},\ \hiki{p}{integer}}{\out{integer}}\\
   \spacing
   % document of basic document
   \quad $a_nx^n + \cdots + a_1x + a_0 \equiv 0 \pmod{\param{p}}$の根の人るを返す。 \\
   \spacing
   % added document
   \quad すべての根を得たいのなら\linkingone{equation}{allroots\_Fp}を使ってください。\\
   \spacing
   % input, output document
   \quad \param{f}は\linkingone{equation}{integer}の\linkingone{equation}{poly\_list}でなければならない。
   さらに\param{p}は素数。 \\
   \quad　根が一つもなければこの関数は何も返さない。\\
%
  \subsection{allroots\_Fp -- solve congruent equation modulo p}\linkedone{equation}{allroots\_Fp}
   \func{allroots\_Fp}{\hiki{f}{\linkingone{equation}{poly\_list}},\ \hiki{p}{integer}}{\out{integer}}\\
   \spacing
   % document of basic document
   \quad $a_nx^n + \cdots + a_1x + a_0 \equiv 0 \pmod{\param{p}}$.のすべての根を返す。\\
   \spacing
   % added document
   %\spacing
   % input, output document
   \quad \param{f}は\linkingone{equation}{integer}の\linkingone{equation}{poly\_list}でなければならない。
   さらに\param{p}は素数。 \\
   \quad 根が一つもないときはこの関数はからのリストを返す。\\
%
\begin{ex}
>>> equation.e1([1, 2])
-0.5
>>> equation.e1([1j, 2])
-0.5j
>>> equation.e1_ZnZ([3, 2], 5)
1
>>> equation.e2([-3, 1, 1])
(1.3027756377319946, -2.3027756377319948)
>>> equation.e2_Fp([-3, 1, 1], 13)
[6, 6]
>>> equation.e3([1, 1, 2, 1])
[(-0.12256116687665397-0.74486176661974479j), 
(-1.7548776662466921+1.8041124150158794e-16j), 
(-0.12256116687665375+0.74486176661974468j)]
>>> equation.e3_Fp([1, 1, 2, 1], 7)
[3]
>>> equation.Newton([-3, 2, 1, 1])
0.84373427789806899
>>> equation.Newton([-3, 2, 1, 1], 2)
0.84373427789806899
>>> equation.Newton([-3, 2, 1, 1], 2, 1000)
0.84373427789806899
>>> equation.SimMethod([-3, 2, 1, 1])
[(0.84373427789806887+0j), 
(-0.92186713894903438+1.6449263775999723j), 
(-0.92186713894903438-1.6449263775999723j)]
>>> equation.root_Fp([-3, 2, 1, 1], 7)
>>> equation.root_Fp([-3, 2, 1, 1], 11)
9L
>>> equation.allroots_Fp([-3, 2, 1, 1], 7)
[]
>>> equation.allroots_Fp([-3, 2, 1, 1], 11)
[9L]
>>> equation.allroots_Fp([-3, 2, 1, 1], 13)
[3L, 7L, 2L]
\end{ex}%Don't indent!(indent causes an error.)
\C

%---------- end document ---------- %

\input{../footer}
