\documentclass{report}

\input{../header_class}

%---------- start document ---------- %
 \section{factor.util -- utilities for factorization}\linkedzero{factor.util}
 \begin{itemize}
   \item {\bf Classes}
   \begin{itemize}
     \item \linkingone{factor.util}{FactoringInteger}
     \item \linkingone{factor.util}{FactoringMethod}
   \end{itemize}
 \end{itemize}

 This module uses following type:
 \begin{description}
   \item[factorlist]\linkedone{factor.util}{factorlist}:\\
     \param{factorlist} is a list which consists of pairs {\tt (base, index)}.
     Each pair means \(base^{index}\).
     The product of those terms expresses whole prime factorization.
 \end{description}

\C

 \subsection{FactoringInteger -- keeping track of factorization}\linkedone{factor.util}{FactoringInteger}
 \initialize
  \func{FactoringInteger}{\hiki{number}{integer}}{\out{FactoringInteger}}\\
  \spacing
  % document of basic document
  \quad This is the base class for factoring integers.\\
  \spacing
  % added document
  \quad  \param{number} is stored in the attribute \linkingtwo{factor.util}{FactoringInteger}{number}. The factors will be stored in the attribute \linkingtwo{factor.util}{FactoringInteger}{factors}, and primality of factors will be tracked in the attribute \linkingtwo{factor.util}{FactoringInteger}{primality}.\\
  \spacing
  % input/output document
  \quad The given \param{number} must be a composite number.\\
  \begin{at}
    \item[number]\linkedtwo{factor.util}{FactoringInteger}{number}:\\ The composite number.
    \item[factors]\linkedtwo{factor.util}{FactoringInteger}{factors}:\\ Factors known at the time being referred.
    \item[primality]\linkedtwo{factor.util}{FactoringInteger}{primality}:\\ A dictionary of primality information of known factors.
      {\tt True} if the factor is prime, {\tt False} composite, or {\tt None} undetermined.
  \end{at}
%   \begin{op}
%     \verb+A==B+ & Return whether M and N are equal or not.\\
%   \end{op} 
% \begin{ex}
% >>> A = factor.util.FactoringInteger((1,2))
% >>> print A
% (1, 2)
% >>> A.point
% (1, 2)
% >>>
% \end{ex}%Don't indent!
  \method
  \subsubsection{getNextTarget -- next target}\linkedtwo{factor.util}{FactoringInteger}{getNextTarget}
   \func{getNextTarget}{\param{self},\ \hikiopt{cond}{function}{{\tt None}}}{\out{integer}}\\
   \spacing
   % document of basic document
   \quad Return the next target which meets \param{cond}.\\
   \spacing
   % added document
   If \param{cond} is not specified, then the next target is a composite (or undetermined) factor of \linkingtwo{factor.util}{FactoringInteger}{number}.\\
   \spacing
   % input, output document
   \quad \param{cond} should be a binary predicate whose arguments are base and index.\\
   \quad If there is no target factor, \linklibraryone{exceptions\#exceptions.LookupError}{LookupError} will be raised.\\
%
 \subsubsection{getResult -- result of factorization}\linkedtwo{factor.util}{FactoringInteger}{getResult}
   \func{getResult}{\param{self}}{\out{\linkingone{factor.util}{factors}}}\\
   \spacing
   % document of basic document
   \quad \linkingtwo{factor.util}{FactoringInteger}{number}の因数分解をする。\\
%
 \subsubsection{register -- register a new factor}\linkedtwo{factor.util}{FactoringInteger}{register}
   \func{register}{\param{self},\ \hiki{divisor}{integer},\ \hikiopt{isprime}{bool}{{\tt None}}}{}\\
   \spacing
    \param{divisor}が本当にある数を割るとき、
   \linkingtwo{factor.util}{FactoringInteger}{number}の\param{divisor}を記憶する。\\
   \spacing
   %added document
   \quad その数は\param{divisor}により可能な限り割られる。\\
   \spacing
   % input/output document
   \param{isprime} tells the primality of the
   \param{divisor} (default to undetermined).\\
%
 \subsubsection{sortFactors -- sort factors}\linkedtwo{factor.util}{FactoringInteger}{sortFactors}
   \func{sortFactors}{\param{self}}{}
   \spacing
   \quad 要素のリストを並べる。\\
   \spacing
    % added document
    \quad この関数は\linkingtwo{factor.util}{FactoringInteger}{getResult}に関係している。\\
%
\begin{ex}
>>> A = factor.util.FactoringInteger(100)
>>> A.getNextTarget()
100
>>> A.getResult()
[(100, 1)]
>>> A.register(5, True)
>>> A.getResult()
[(5, 2), (4, 1)]
>>> A.sortFactors()
>>> A.getResult()
[(4, 1), (5, 2)
>>> A.primality
{4: None, 5: True}
>>> A.getNextTarget()
4
\end{ex}%Don't indent!
\C

 \subsection{FactoringMethod -- method of factorization}\linkedone{factor.util}{FactoringMethod}
 \initialize
  \func{FactoringMethod}{}{\out{FactoringMethod}}\\
  \spacing
  % document of basic document
  \quad Base class of factoring methods.\\
  \spacing
  % added document
  \quad すべての方法は\linkingzero{factor.methods}で定義されている。
  implemented as derived classes of this class. この方法は\linkingtwo{factor.util}{FactoringMethod}{factor}と呼ぶこともある。 
 　他の方法は\\
  \method
  \subsubsection{factor -- do factorization}\linkedtwo{factor.util}{FactoringMethod}{factor}
   \func{factor}{\param{self},\ %
     \hiki{number}{integer},\ %
     \hikiopt{return\_type}{str}{'list'},\ %
     \hikiopt{need\_sort}{bool}{False}
   }{\out{\linkingone{factor.util}{factorlist}}}\\
   \spacing
   % document of basic document
   \quad 与えられた正の整数\param{number}の因数分解を行う。\\
   \quad 不履行の場合は\linkingone{factor.util}{factorlist}を返す。\\
   \quad A keyword option \param{return\_type} can be as the following:
   \begin{enumerate}
   \item {\tt 'list'} for default type (\linkingone{factor.util}{factorlist}).
   \item {\tt 'tracker'} for \linkingone{factor.util}{FactoringInteger}.
   \end{enumerate}
   \quad Another keyword option \param{need\_sort} is Boolean:
   {\tt True} to sort the result.
   This should be specified with {\tt return\_type='list'}.\\
%
  \subsubsection{\negok continue\_factor -- continue factorization}\linkedtwo{factor.util}{FactoringMethod}{continue\_factor}
  \func{continue\_factor}{\param{self},\ %
    \hiki{tracker}{\linkingone{factor.util}{FactoringInteger}},\ %
    \hikiopt{return\_type}{str}{'tracker'},\ %
    \hikiopt{primeq}{func}{\linkingone{prime}{primeq}}
  }{\out{\linkingone{factor.util}{FactoringInteger}}}\\
  \spacing
  \quad Continue factoring of the given \param{tracker} and return the
  result of factorization.\\
  \spacing
  \quad The default returned type is \linkingone{factor.util}{FactoringInteger},
  but if \param{return\_type} is specified as {\tt 'list'}
  then it returns \linkingone{factor.util}{factorlist}.
  The primality is judged by a function specified in \param{primeq}
  optional keyword argument, which default is \linkingone{prime}{primeq}.\\
%
  \subsubsection{\negok find -- find a factor}\linkedtwo{factor.util}{FactoringMethod}{find}
  \func{find}{\param{self},\ %
    \hiki{target}{integer},\ %
    **\param{options}
  }{\out{integer}}\\
  \spacing
  \quad \param{target}から要素を探す。\\
  \spacing
  \quad この方法は優先されるべきである。または\linkingtwo{factor.util}{FactoringMethod}{factor}法も\\
%
  \subsubsection{\negok generate -- generate prime factors}\linkedtwo{factor.util}{FactoringMethod}{generate}
  \func{generate}{\param{self},\ %
    \hiki{target}{integer},\ %
    **\param{options}
  }{\out{integer}}\\
  \spacing
 % basic document
  \quad Generate prime factors of the \param{target} number with their valuations.\\
 \spacing
 % added document
  \quad この関数が{\tt (1, 1)}を返したら因数分解は不完全であることを示す。
  to indicate the factorization is incomplete.\\
  This method has to be overridden, or \linkingtwo{factor.util}{FactoringMethod}{factor} method should be overridden not to call this method.\\
\C

%---------- end document ---------- %

\input{../footer}
