\input{../header_class}

%---------- start document ---------- %
 \section{factor.misc -- miscellaneous functions related factoring}\linkedzero{factor.misc}
 \begin{itemize}
   \item {\bf Functions}
     \begin{itemize}
       \item \linkingone{factor.misc}{allDivisors}
       \item \linkingone{factor.misc}{primeDivisors}
       \item \linkingone{factor.misc}{primePowerTest}
       \item \linkingone{factor.misc}{squarePart}
     \end{itemize}
   \item {\bf Classes}
   \begin{itemize}
     \item \linkingone{factor.misc}{FactoredInteger}
   \end{itemize}
 \end{itemize}
%
  \subsection{allDivisors -- all divisors}\linkedone{factor.misc}{allDivisors}
   \func{allDivisors}{\hiki{n}{integer}}{\out{list}}\\
   \spacing
   % document of basic document
   \quad  \param{n}で割ったすべての要素の値をリストとして返す。\\
%
  \subsection{primeDivisors -- prime divisors}\linkedone{factor.misc}{primeDivisors}
   \func{primeDivisors}{\hiki{n}{integer}}{\out{list}}\\
   \spacing
   % document of basic document
   \quad \param{n}で割ったすべての素数である要素の値をリストとして返す。\\
%
  \subsection{primePowerTest -- prime power test}\linkedone{factor.misc}{primePowerTest}
   \func{primePowerTest}{\hiki{n}{integer}}{(\out{integer},\ \out{integer})}\\
   \spacing
   \quad Judge whether \param{n} is of the form \(p^k\) with a prime \(p\)
   もし正しいのなら{\tt (p, k)}を返し、 さもなければ {\tt (n, 0)}を返す。\\
   \spacing
   \quad この関数はAlgo. 1.7.5 in \cite{Cohen1}に基づいている。\\
%
  \subsection{squarePart -- square part}\linkedone{factor.misc}{squarePart}
   \func{squarePart}{\hiki{n}{integer}}{\out{integer}}\\
   \spacing
   \quad \param{n}を割り切る最大の整数の二乗の値を返す。
%
\begin{ex}
>>> factor.misc.allDivisors(1001)
[1, 7, 11, 13L, 77, 91L, 143L, 1001L]
>>> factor.misc.primeDivisors(100)
[2, 5]
>>> factor.misc.primePowerTest(128)
(2, 7)
>>> factor.misc.squarePart(128)
8L
\end{ex}%Don't indent!(indent causes an error.)
\C

  \subsection{FactoredInteger -- integer with its factorization}\linkedone{factor.misc}{FactoredInteger}
  \initialize
   \func{FactoredInteger}{\hiki{integer}{integer},\ \hikiopt{factors}{dict}{\{\}}}{\out{FactoredInteger}}\\
   \spacing
   \quad Integer with its factorization information.\\
   \spacing
   \quad If \param{factors} is given, it is a dict of type
   {\tt {prime:exponent}} and the product of \(prime^{exponent}\)
   is equal to the \param{integer}. Otherwise, factorization is
   carried out in initialization.\\

   \func{from\_partial\_factorization}{\param{cls},\ \hiki{integer}{integer},\ \hiki{partial}{dict}}{\out{FactoredInteger}}\\
   \spacing
   \quad A class method to create a new \linkingone{factor.misc}{FactoredInteger} object from partial factorization information \param{partial}.\\
   \begin{op}
     \verb+F * G+ & multiplication (other operand can be an int)\\
     \verb+F ** n+ & powering\\
     \verb+F == G+ & equal\\
     \verb+F != G+ & not equal\\
     \verb+F % G+ & remainder (the result is an int)\\
     \verb+F // G+ & same as \linkingtwo{factor.misc}{FactoredInteger}{exact\_division} method\\
     \verb+str(F)+ & string\\
     \verb+int(F)+ & convert to Python integer (forgetting factorization)\\
   \end{op}
   \method
   \subsubsection{is\_divisible\_by}\linkedtwo{factor.misc}{FactoredInteger}{is\_divisible\_by}
   \func{is\_divisible\_by}{\param{self},\ \hiki{other}{integer/\linkingone{factor.misc}{FactoredInteger}}}{\out{bool}}\\
   \spacing
   \quad \param{other}が\param{self}割り切ったのならTrueと返す。\\

   \subsubsection{exact\_division}\linkedtwo{factor.misc}{FactoredInteger}{exact\_division}
   \func{exact\_division}{\param{self},\ \hiki{other}{integer/\linkingone{factor.misc}{FactoredInteger}}}{\out{\linkingone{factor.misc}{FactoredInteger}}}\\
   \spacing
   \quad \param{other}で割るとき、\param{other}は\param{self}で必ず割り切る。\\

   \subsubsection{divisors}\linkedtwo{factor.misc}{FactoredInteger}{divisors}
   \func{divisors}{\param{self}}{\out{list}}\\
   \spacing
   \quad すべての除数をリストとして返す。\\

   \subsubsection{proper\_divisors}\linkedtwo{factor.misc}{FactoredInteger}{proper\_divisors}
   \func{proper\_divisors}{\param{self}}{\out{list}}\\
   \spacing
   \quad \(1\)と\param{self}\\を含まないすすべての除数をリストとして返す。\\

   \subsubsection{prime\_divisors}\linkedtwo{factor.misc}{FactoredInteger}{prime\_divisors}
   \func{prime\_divisors}{\param{self}}{\out{list}}\\
   \spacing
   \quad すべての素数の除数をリストとして返す。\\

   \subsubsection{square\_part}\linkedtwo{factor.misc}{FactoredInteger}{square\_part}
   \func{square\_part}{\param{self},\ \hikiopt{asfactored}{bool}{False}}{\out{integer/\linkingone{factor.misc}{FactoredInteger object}}}\\
   \spacing
   \quad \param{self}を割る最大の整数の値を返す。\\
   \spacing
   \quad If an optional argument \param{asfactored} is true,
   then the result is also a \linkingone{factor.misc}{FactoredInteger object}. (default is False)\\

   \subsubsection{squarefree\_part}\linkedtwo{factor.misc}{FactoredInteger}{squarefree\_part}
   \func{squarefree\_part}{\param{self},\ \hikiopt{asfactored}{bool}{False}}{\out{integer/\linkingone{factor.misc}{FactoredInteger object}}}\\
   \spacing
   \quad \param{self}を割り、二乗にならない最大の整数の値を返す。\\
   \spacing
   \quad If an optional argument \param{asfactored} is true,
   then the result is also a \linkingone{factor.misc}{FactoredInteger object} object. (default is False)\\

   \subsubsection{copy}\linkedtwo{factor.misc}{FactoredInteger}{copy}
   \func{copy}{\param{self}}{\out{\linkingone{factor.misc}{FactoredInteger object}}}\\
   \spacing
   \quad 自分自身をコピーした値を返す。\\

%---------- end document ---------- %

\input{../footer}
